### 2014-11-13 tex/heap.tex
Minor edits

\subsection{Summary Heaps as Bipartite Graphs}
A novel contribution of summary heaps for symbolic execution is the
labeled bipartite graph representation of the heap which enables a
summary heap to group heaps together that follow the same control flow
to a given point of execution. The graph structure is able to capture
group membership and compute value sets using entirely non-recursive
local look up. Additionally, updates on the heap do not require
rewriting the path condition or any constraints in summary heap.

The bipartite graph itself consists of references, $\cfgnt{r}$, and
constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
expressed in the location map, $\cfgnt{L}$, and the reference map,
$\cfgnt{R}$. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$
are treated as partial functions where $\cfgnt{L}(r) =
\{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs in
the heap associated with the given reference, and
$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
associated with the given location-field pair in the heap. Predicate
calculus is used to describe the more complex updates to the heap in
the semantics.

There are several properties of the summary heap enforced by the
rewrite rules that are invariant and important to the correctness
proofs presented in \secref{sec:bisim}: \emph{reference partitions},
\emph{immutable references}, \emph{determinism}, \emph{type
  consistency}, and \emph{null and uninitialized}.

\emph{Reference partitions} are new references drawn from
  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
  continuations. The references strictly increase in value on each
  call, and modular arithmetic is used to determine the partition to
  which a reference belongs.
\begin{compactdesc}
\item[Input heap] these references have two
  interpretations: one as a literal and another as a variable. First,
  an input heap reference is a literal, and that literal is a node in
  the summary heap. Second, an input heap reference is a variable, and
  that variable is a term in any number of constraints that label
  edges in the summary heap. Only input heap references and the
  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
\item[Auxiliary literals] these references are only used to define additional structure in
  the bipartite graph and are not part of any constraint and do not appear
  in any environment, expression, or continuation.
\item[Stack references] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation. These are not part of any constraint.
\end{compactdesc}
Reference partitions are a critical piece to the existence proof of a
bisimilation between the summary heap algorithm and generalized
symbolic execution (see \secref{sec:bisim}).

\emph{Immutable references} means that a reference does not change in the
location map. It always points to the same set of constraint location
pairs. This property ensures that constraints never need to be
rewritten as the program evolves its state.

@@

For example, if the solver assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$
such that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists
some location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
that
\begin{compactitem}
\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
\item $\phi$ and $\phi^\prime$ are true under aliasing assignments from the solver.
\end{compactitem}
In this way, the graph groups heaps with the conditions under which
those heaps exist. This representation, by virtue of the reference
partitions, separates the constraint problem from the morphology
problem: it is possible to update the heap without having to rewrite
constraints. Without this separation, it would not be possible to
lazily initialize heap locations along a program path.

@@

To show the heap summary algorithm is sound and complete with respect
to properties proved by generalized symbolic execution, we refer to
the generalized symbolic execution with lazy initialization machine by
the relation $\rgse$ or $p \rgse p^\prime$, and to the new summary
heap algorithm machine by $\rsym$ or $q \rsym q^\prime$. Both machines
use the summary heap structure, and for simplicity,
both use lazy initialization as opposed to lazier or lazier\#.

Due to space restrictions, the full operational semantics for
generalized symbolic execution with lazy initialization for Javalite
are presented in the supplemental document. We also present the
portion of the Javalite rewrite rules which are common to both
machines in the supplementary document. In the next section, we
present the rewrite rules specific to the new summary heap algorithm
for symbolic execution.

>>>>

\subsection{Summary Heaps as Bipartite Graphs}
A novel contribution of summary heaps for symbolic execution is the
labeled bipartite graph representation of the heap which enables a
summary heap to group heaps together that follow the same control flow
to a given point of execution. The graph structure is able to capture
group membership and compute value sets using entirely non-recursive
local look up. Additionally, updates on the heap do not require
rewriting the path condition or any constraints in the summary heap.

The bipartite graph itself consists of references, $\cfgnt{r}$, and
constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
expressed in the location map, $\cfgnt{L}$, and the reference map,
$\cfgnt{R}$. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$
are treated as partial functions where $\cfgnt{L}(r) =
\{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs in
the heap associated with the given reference, and
$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
associated with the given location-field pair in the heap.

There are several properties of the summary heap enforced by the
rewrite rules that are invariant and important to the correctness
proofs presented in \secref{sec:bisim}: \emph{reference partitions},
\emph{immutability}, \emph{determinism}, \emph{type
  consistency}, and \emph{null and uninitialized}.

\emph{Reference partitions} are new references drawn from
  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
  continuations. The references strictly increase in value on each
  call, and modular arithmetic is used to determine the partition to
  which a reference belongs.
\begin{compactdesc}
\item[Input heap:] these references have two
  interpretations: one as a literal and another as a variable. First,
  an input heap reference is a literal, and that literal is a node in
  the summary heap. Second, an input heap reference is a variable, and
  that variable is a term in any number of constraints that label
  edges in the summary heap. Only input heap references and the
  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
\item[Auxiliary literals:] these references are only used to define additional structure in
  the bipartite graph and are not part of any constraint and do not appear
  in any environment, expression, or continuation.
\item[Stack references:] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation. These are not part of any constraint.
\end{compactdesc}
Reference partitions are a critical piece to the existence proof of a
bisimilation between the summary heap algorithm and generalized
symbolic execution (see \secref{sec:bisim}).

\emph{Immutability} means that a reference does not change in the
location map. It always points to the same set of constraint location
pairs. This property ensures that constraints never need to be
rewritten as the program evolves its state.

@@

For example, if the solver assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$
such that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists
some location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
that
\begin{compactitem}
\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
\item $\phi$ and $\phi^\prime$ hold in aliasing assignments from the solver.
\end{compactitem}
In this way, the graph groups heaps with the conditions under which
those heaps exist. This representation separates the constraint
problem from the morphology problem: it is possible to update the heap
without having to rewrite constraints. Without this separation, it
would not be possible to lazily initialize heap locations along a
program path.

@@

To show the heap summary algorithm is sound and complete with respect
to properties proved by GSE, we define a transition relation that
relates states according GSE and refer to it as $\rgse$ or $p \rgse
p^\prime$. Similarly we define for the new summary heap algorithm
$\rsym$ or $q \rsym q^\prime$. For simplicity, both use lazy
initialization as opposed to lazier or lazier\#.

The full operational semantics for $\rgse$ are in the supplemental
document. In the next section, we present the rewrite rules specific
to $\rsym$.

### 2014-11-13 tex/javalite.tex
Minor edits

Javalite is a syntactic machine defined as rewrites on a string.  The
semantics are small-step using the CESK architecture with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (S)tore for the heap, and a (K)ontinuation for what
is to be executed next.  In this work we change the semantics of the original
 Javalite machine and its machine syntax to represent (i) generalized
symbolic execution~\cite{GSE03}, and (ii) the summary heap algorithm
presented in this work.

>>>>

Javalite is a syntactic machine defined as rewrites on a string.  The
semantics are small-step using the CESK architecture with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (S)tore for the heap, and a (K)ontinuation for what
is to be executed next.  In this work we change the semantics of the original
 Javalite machine and its machine syntax to represent (i) GSE~\cite{GSE03}, and (ii) the summary heap algorithm
presented in this work.
